---
title: "Daily and Weekly Summaries"
---

Purpose: Generate weekly summaries to use in Gg framework

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(sf)
library(mapview)
library(knitr)
library(fasstr)
library(RColorBrewer)
library(scales)
library(dygraphs)
library(hydroEvents)
library(GGally)
library(dataRetrieval)
library(ggpubr)
library(DT)
library(colorspace)
```


## Site info and daily data
```{r}
# site information
siteinfo <- read_csv("C:/Users/jbaldock/OneDrive - DOI/Documents/USGS/EcoDrought/EcoDrought Working/Data/EcoDrought_SiteInformation.csv")

# flow/yield (and temp) data 
dat <- read_csv("C:/Users/jbaldock/OneDrive - DOI/Documents/USGS/EcoDrought/EcoDrought Working/Data/EcoDrought_FlowTempData_DailyWeekly.csv")

# add water/climate year variables and fill missing dates
dat <- add_date_variables(dat, dates = date, water_year_start = 4)
dat <- fill_missing_dates(dat, dates = date, groups = site_name)
str(dat)
```

Define G-g clusters/sub-basins
```{r}
siteinfo2 <- siteinfo %>% 
  filter(!site_name %in% c("WoundedBuckCreek", "Brackett Creek", "South River Conway NWIS", 
                           "Shields River nr Livingston NWIS", "North Fork Flathead River NWIS", 
                           "Pacific Creek at Moran NWIS")) %>%
  mutate(designation = ifelse(site_name %in% c("Donner Blitzen River nr Frenchglen NWIS", 
                                               "BigCreekLower", "CoalCreekLower", "McGeeCreekLower", 
                                               "West Brook NWIS", "West Brook 0", 
                                               "Paine Run 10", "Staunton River 10", "Piney River 10", 
                                               "Shields River Valley Ranch", "Shields River ab Smith NWIS", 
                                               "EF Duck Creek be HF",
                                               "Spread Creek Dam"), "big", "little"))
```

Map focal sites/subbasins
```{r}
siteinfo_sp <- st_as_sf(siteinfo2, coords = c("long", "lat"), crs = 4326)
mapview(siteinfo_sp, zcol = "designation")
```

```{r}
datatable(siteinfo2 %>% 
            arrange(region, basin, subbasin, designation) %>% 
            mutate(lat = round(lat, digits = 2), 
                   long = round(long, digits = 2), 
                   area_sqmi = round(area_sqmi, digits = 2), 
                   elev_ft = round(elev_ft, digits = 0)),
          caption = "EcoDrought monitoring locations and metadata.")
```



## View daily data

View daily time series data by sub-basin (little and medium g's only)

::: panel-tabset
### West Brook
```{r, echo=FALSE}
dat %>% filter(site_name %in% unlist(siteinfo2 %>% filter(subbasin == "West Brook") %>% select(site_name))) %>% mutate(logYield = log(Yield_filled_mm)) %>% select(date, site_name, logYield) %>% spread(key = site_name, value = logYield) %>% dygraph() %>% dyRangeSelector() %>% dyAxis("y", label = "ln(Yield, mm)")
```
### Paine Run
```{r, echo=FALSE}
dat %>% filter(site_name %in% unlist(siteinfo2 %>% filter(subbasin == "Paine Run") %>% select(site_name)), date >= as_date("2018-11-07")) %>% mutate(logYield = log(Yield_filled_mm)) %>% select(date, site_name, logYield) %>% spread(key = site_name, value = logYield) %>% dygraph() %>% dyRangeSelector() %>% dyAxis("y", label = "ln(Yield, mm)")
```
### Piney River
```{r, echo=FALSE}
dat %>% filter(site_name %in% unlist(siteinfo2 %>% filter(subbasin == "Piney River") %>% select(site_name))) %>% mutate(logYield = log(Yield_filled_mm)) %>% select(date, site_name, logYield) %>% spread(key = site_name, value = logYield) %>% dygraph() %>% dyRangeSelector() %>% dyAxis("y", label = "ln(Yield, mm)")
```
### Staunton River
```{r, echo=FALSE}
dat %>% filter(site_name %in% unlist(siteinfo2 %>% filter(subbasin == "Staunton River") %>% select(site_name)), date >= as_date("2018-11-07")) %>% mutate(logYield = log(Yield_filled_mm)) %>% select(date, site_name, logYield) %>% spread(key = site_name, value = logYield) %>% dygraph() %>% dyRangeSelector() %>% dyAxis("y", label = "ln(Yield, mm)")
```
### Big Creek
```{r, echo=FALSE}
dat %>% filter(site_name %in% unlist(siteinfo2 %>% filter(subbasin == "Big Creek") %>% select(site_name))) %>% mutate(logYield = log(Yield_filled_mm)) %>% select(date, site_name, logYield) %>% spread(key = site_name, value = logYield) %>% dygraph() %>% dyRangeSelector() %>% dyAxis("y", label = "ln(Yield, mm)")
```
### Coal Creek
```{r, echo=FALSE}
dat %>% filter(site_name %in% unlist(siteinfo2 %>% filter(subbasin == "Coal Creek") %>% select(site_name))) %>% mutate(logYield = log(Yield_filled_mm)) %>% select(date, site_name, logYield) %>% spread(key = site_name, value = logYield) %>% dygraph() %>% dyRangeSelector() %>% dyAxis("y", label = "ln(Yield, mm)")
```
### McGee Creek
```{r, echo=FALSE}
dat %>% filter(site_name %in% unlist(siteinfo2 %>% filter(subbasin == "McGee Creek") %>% select(site_name))) %>% mutate(logYield = log(Yield_filled_mm)) %>% select(date, site_name, logYield) %>% spread(key = site_name, value = logYield) %>% dygraph() %>% dyRangeSelector() %>% dyAxis("y", label = "ln(Yield, mm)")
```
### Snake River
```{r, echo=FALSE}
dat %>% filter(site_name %in% unlist(siteinfo2 %>% filter(subbasin == "Snake River") %>% select(site_name))) %>% mutate(logYield = log(Yield_filled_mm)) %>% select(date, site_name, logYield) %>% spread(key = site_name, value = logYield) %>% dygraph() %>% dyRangeSelector() %>% dyAxis("y", label = "ln(Yield, mm)")
```
### Shields River
```{r, echo=FALSE}
dat %>% filter(site_name %in% unlist(siteinfo2 %>% filter(subbasin == "Shields River") %>% select(site_name))) %>% mutate(logYield = log(Yield_filled_mm)) %>% select(date, site_name, logYield) %>% spread(key = site_name, value = logYield) %>% dygraph() %>% dyRangeSelector() %>% dyAxis("y", label = "ln(Yield, mm)")
```
### Duck Creek
```{r, echo=FALSE}
dat %>% filter(designation %in% c("little", "medium"), subbasin == "Duck Creek") %>% mutate(logYield = log(Yield_filled_mm)) %>% select(date, site_name, logYield) %>% spread(key = site_name, value = logYield) %>% dygraph() %>% dyRangeSelector() %>% dyAxis("y", label = "ln(Yield, mm)")
```
### Donner Blitzen
```{r, echo=FALSE}
dat %>% filter(site_name %in% unlist(siteinfo2 %>% filter(subbasin == "Donner Blitzen") %>% select(site_name)), date >= as_date("2019-07-23")) %>% mutate(logYield = log(Yield_filled_mm)) %>% select(date, site_name, logYield) %>% spread(key = site_name, value = logYield) %>% dygraph() %>% dyRangeSelector() %>% dyAxis("y", label = "ln(Yield, mm)")
```
:::


## Daily gG

### Organize data

#### Get big and little g's

Define focal basins
```{r}
focalbasins <- c("West Brook", "Paine Run", "Staunton River", "Big Creek", "Coal Creek", "McGee Creek", "Donner Blitzen", "Shields River", "Snake River", "Duck Creek")
```

Recode co-located gages and designate big and little g data:
```{r}
dat_day_big <- dat %>% 
  mutate(site_name = dplyr::recode(site_name, "Leidy Creek Mouth NWIS" = "Leidy Creek Mouth", "SF Spread Creek Lower NWIS" = "SF Spread Creek Lower", "Dugout Creek NWIS" = "Dugout Creek", "Shields River ab Smith NWIS" = "Shields River Valley Ranch")) %>%
  filter(site_name %in% c("Donner Blitzen River nr Frenchglen NWIS", "BigCreekLower", "CoalCreekLower", "McGeeCreekLower", "West Brook NWIS", "Paine Run 10", "Staunton River 10", "Spread Creek Dam", "Shields River Valley Ranch", "EF Duck Creek be HF"))

dat_day_little <- dat %>% 
  mutate(site_name = dplyr::recode(site_name, "Leidy Creek Mouth NWIS" = "Leidy Creek Mouth", "SF Spread Creek Lower NWIS" = "SF Spread Creek Lower", "Dugout Creek NWIS" = "Dugout Creek", "Shields River ab Smith NWIS" = "Shields River Valley Ranch")) %>%
  filter(subbasin %in% focalbasins, site_name %in% unlist(siteinfo2 %>% filter(designation == "little") %>% select(site_name)))

#c("Donner Blitzen River nr Frenchglen NWIS",  "BigCreekLower", "Big Creek NWIS", "CoalCreekLower", "McGeeCreekLower", "West Brook NWIS", "Avery Brook NWIS", "West Brook 0", "Paine Run 10", "Staunton River 10")
```

Big G sites
```{r}
unique(dat_day_big$site_name)
```

Little g sites
```{r}
unique(dat_day_little$site_name)
```

#### Zero flow proportion

How common is 0 flow and which sites experience drying?
```{r}
paste(round((nrow(dat %>% filter(Yield_filled_mm == 0)) / nrow(dat))*100, digits = 3), "% of all flow observations are 0 cfs/yield.", sep = "")

dat %>% filter(Yield_filled_mm == 0) %>% group_by(site_name) %>% summarize(numdays_0flow = n()) %>% left_join(dat %>% filter(!is.na(Yield_filled_mm)) %>% group_by(site_name) %>% summarize(numdays = n())) %>% mutate(prop_0flow = numdays_0flow / numdays) %>% kable()
```

Days with zero flow are exceptionally rare in our dataset. Thus, drop all days of zero flow for downstream analysis b/c of issues associated with log transforming 0s. 

#### Join data

Join big and little g data:
```{r}
dat_day_join <- dat_day_little %>% 
  filter(Yield_filled_mm > 0 ) %>%
  select(basin, subbasin, site_name, date, Yield_filled_mm) %>% 
  rename(site_name_little = site_name, yield_little = Yield_filled_mm) %>% 
  left_join(dat_day_big %>% filter(Yield_filled_mm > 0 ) %>%
              select(basin, subbasin, site_name, date, Yield_filled_mm) %>%
              rename(site_name_big = site_name, yield_big = Yield_filled_mm)) %>%
  filter(!is.na(yield_big)) %>%
  mutate(yield_little_log = log(yield_little),
         yield_big_log = log(yield_big))
head(dat_day_join)
```

View sample size (number of days) per site:
```{r}
datatable(dat_day_join %>% group_by(subbasin, site_name_little) %>% summarize(numdays = n()),
          caption = "Sample size (number of days) per site.")
```


### View gG - sites combined

::: panel-tabset
#### West Brook
```{r}
dat_day_join %>% filter(subbasin == "West Brook") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Big Creek
```{r}
dat_day_join %>% filter(subbasin == "Big Creek") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Coal Creek
```{r}
dat_day_join %>% filter(subbasin == "Coal Creek") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### McGee Creek
```{r}
dat_day_join %>% filter(subbasin == "McGee Creek") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Paine Run
```{r}
dat_day_join %>% filter(subbasin == "Paine Run") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Staunton River
```{r}
dat_day_join %>% filter(subbasin == "Staunton River") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Donner Blitzen
```{r}
dat_day_join %>% filter(subbasin == "Donner Blitzen") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Snake River
```{r}
dat_day_join %>% filter(subbasin == "Snake River") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Shields River
```{r}
dat_day_join %>% filter(subbasin == "Shields River") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Duck Creek
```{r}
dat_day_join %>% filter(subbasin == "Duck Creek") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```

:::


### View gG - facet by site

::: panel-tabset
#### West Brook
```{r fig.width=8, fig.height=9}
dat_day_join %>% filter(subbasin == "West Brook") %>% mutate(year = as.factor(year(date))) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.15) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little, ncol = 3, nrow = 4)
```
#### Big Creek
```{r fig.width=8, fig.height=9}
dat_day_join %>% filter(subbasin == "Big Creek") %>% mutate(year = as.factor(year(date))) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.15) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little, ncol = 3, nrow = 4)
```
#### Coal Creek
```{r fig.width=8, fig.height=5}
dat_day_join %>% filter(subbasin == "Coal Creek") %>% mutate(year = as.factor(year(date))) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.15) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little, ncol = 3)
```
#### McGee Creek
```{r fig.width=6, fig.height=3}
dat_day_join %>% filter(subbasin == "McGee Creek") %>% mutate(year = as.factor(year(date))) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.15) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
#### Paine Run
```{r fig.width=8, fig.height=5}
dat_day_join %>% filter(subbasin == "Paine Run") %>% mutate(year = as.factor(year(date))) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.15) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
#### Staunton River
```{r fig.width=8, fig.height=5}
dat_day_join %>% filter(subbasin == "Staunton River") %>% mutate(year = as.factor(year(date))) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.15) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
#### Donner Blitzen
```{r fig.width=6, fig.height=5}
dat_day_join %>% filter(subbasin == "Donner Blitzen") %>% mutate(year = as.factor(year(date))) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.15) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
#### Snake River
```{r fig.width=8, fig.height=7}
dat_day_join %>% filter(subbasin == "Snake River") %>% mutate(year = as.factor(year(date))) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.15) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
#### Shields River
```{r fig.width=8, fig.height=5}
dat_day_join %>% filter(subbasin == "Shields River") %>% mutate(year = as.factor(year(date))) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.15) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
#### Duck Creek
```{r fig.width=6, fig.height=3}
dat_day_join %>% filter(subbasin == "Duck Creek") %>% mutate(year = as.factor(year(date))) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.15) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
:::


### Hyteresis loops

Create plotting function
```{r}
myplotfun <- function(mysite) {
  print(dat_day_join %>%
  mutate(doy = yday(date), year = year(date)) %>%
  filter(site_name_little == mysite) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = doy)) +
  geom_segment(aes(xend = c(tail(yield_big_log, n = -1), NA), 
                   yend = c(tail(yield_little_log, n = -1), NA)), 
               arrow = arrow(length = unit(0.3, "cm")), color = "black") +
  geom_point() + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  scale_color_gradient2(midpoint = 182, low = "purple3", mid = "orange", high = "purple3") +
  facet_wrap(~year))
}
```

#### West Brook
::: panel-tabset
##### Avery Brook
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Avery Brook")
```
##### Avery Brook NWIS
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Avery Brook NWIS")
```
##### Jimmy Brook
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Jimmy Brook")
```
##### Mitchell Brook
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Mitchell Brook")
```
##### Avery Brook
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Avery Brook")
```
##### Obear Brook Lower
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Obear Brook Lower")
```
##### Sanderson Brook
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Sanderson Brook")
```
##### West Brook Lower
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "West Brook Lower")
```
##### West Brook Reservoir
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "West Brook Reservoir")
```
##### West Brook Upper
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "West Brook Upper")
```
:::


#### Big Creek
::: panel-tabset
##### Big Creek NWIS
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Big Creek NWIS")
```
##### BigCreekMiddle
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "BigCreekMiddle")
```
##### BigCreekUpper
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "BigCreekUpper")
```
##### Hallowat Creek NWIS
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Hallowat Creek NWIS")
```
##### HallowattCreekLower
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "HallowattCreekLower")
```
##### LangfordCreekLower
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "LangfordCreekLower")
```
##### LangfordCreekUpper
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "LangfordCreekUpper")
```
##### NicolaCreek
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "NicolaCreek")
```
##### SkookoleelCreek
```{r fig.width=8, fig.height=4}
myplotfun(mysite = "SkookoleelCreek")
```
##### WernerCreek
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "WernerCreek")
```
:::


#### Staunton River
::: panel-tabset
##### Staunton River 02
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Staunton River 02")
```
##### Staunton River 03
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Staunton River 03")
```
##### Staunton River 06
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Staunton River 06")
```
##### Staunton River 07
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Staunton River 07")
```
##### Staunton River 09
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Staunton River 09")
```
:::


#### Shields River
::: panel-tabset
##### Buck Creek
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Buck Creek")
```
##### Crandall Creek
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Crandall Creek")
```
##### Deep Creek
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Deep Creek")
```
##### Dugout Creek
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Dugout Creek")
```
##### Lodgepole Creek
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Lodgepole Creek")
```
##### Shields River ab Dugout
```{r fig.width=8, fig.height=8}
myplotfun(mysite = "Shields River ab Dugout")
```
:::



Color by rate of change (rising vs falling limbs)
```{r fig.width=8, fig.height=8}


dat_day_join %>%
  mutate(doy = yday(date), year = year(date)) %>%
  filter(site_name_little == "LangfordCreekLower") %>%
  mutate(big_deriv1 = (yield_big_log - lag(yield_big_log)) / (doy - lag(doy))) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = big_deriv1)) +
  geom_segment(aes(xend = c(tail(yield_big_log, n = -1), NA), 
                   yend = c(tail(yield_little_log, n = -1), NA)), 
               arrow = arrow(length = unit(0.3, "cm")), color = "black") +
  geom_point() + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  scale_color_continuous_diverging(palette = "Red-Green") +
  theme_dark()+
  facet_wrap(~year)
# 
# myplotfun <- function(mysite) {
#   print(dat_day_join %>%
#   mutate(doy = yday(date), year = year(date)) %>%
#   filter(site_name_little == mysite) %>%
#   ggplot(aes(x = yield_big_log, y = yield_little_log, color = doy)) +
#   geom_segment(aes(xend = c(tail(yield_big_log, n = -1), NA), 
#                    yend = c(tail(yield_little_log, n = -1), NA)), 
#                arrow = arrow(length = unit(0.3, "cm")), color = "black") +
#   geom_point() + 
#   geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
#   scale_color_gradient2(midpoint = 182, low = "purple3", mid = "orange", high = "purple3") +
#   facet_wrap(~year))
# }
```


## Weekly gG

### Organize data

Summarize daily data as weekly means:
```{r}
dat_week <- dat %>% mutate(year = year(date), week = week(date)) %>% filter(!is.na(Yield_filled_mm)) %>% group_by(basin, subbasin, region, site_name, lat, long, elev_ft, area_sqmi, designation, year, week) %>% summarize(Yield_filled_mm_weekly = sum(Yield_filled_mm, na.rm = TRUE), n = n(), mindate = min(date), maxdate = max(date)) %>% ungroup() %>% filter(n == 7, !is.na(Yield_filled_mm_weekly))
```

#### Get big and little g's

Designate big and little g data:
```{r}
dat_week_big <- dat_week %>% 
  mutate(site_name = dplyr::recode(site_name, "Leidy Creek Mouth NWIS" = "Leidy Creek Mouth", "SF Spread Creek Lower NWIS" = "SF Spread Creek Lower", "Dugout Creek NWIS" = "Dugout Creek", "Shields River ab Smith NWIS" = "Shields River Valley Ranch")) %>%
  filter(site_name %in% c("Donner Blitzen River nr Frenchglen NWIS", "BigCreekLower", "CoalCreekLower", "McGeeCreekLower", "West Brook NWIS", "Paine Run 10", "Staunton River 10", "Spread Creek Dam", "Shields River Valley Ranch", "EF Duck Creek be HF"))

dat_week_little <- dat_week %>% 
  mutate(site_name = dplyr::recode(site_name, "Leidy Creek Mouth NWIS" = "Leidy Creek Mouth", "SF Spread Creek Lower NWIS" = "SF Spread Creek Lower", "Dugout Creek NWIS" = "Dugout Creek", "Shields River ab Smith NWIS" = "Shields River Valley Ranch")) %>%
  filter(subbasin %in% focalbasins, site_name %in% unlist(siteinfo2 %>% filter(designation == "little") %>% select(site_name)))
```

#### Zero flow proportion

How common is 0 flow and which sites experience drying?
```{r}
paste(round((nrow(dat_week %>% filter(Yield_filled_mm_weekly == 0)) / nrow(dat_week))*100, digits = 3), "% of all weekly flow observations are 0 cfs/yield.", sep = "")

dat_week %>% filter(Yield_filled_mm_weekly == 0) %>% group_by(site_name) %>% summarize(numdays_0flow = n()) %>% left_join(dat_week %>% filter(!is.na(Yield_filled_mm_weekly)) %>% group_by(site_name) %>% summarize(numdays = n())) %>% mutate(prop_0flow = numdays_0flow / numdays) %>% kable()
```

#### Join data

Join big and little g data:
```{r}
dat_week_join <- dat_week_little %>% 
  filter(Yield_filled_mm_weekly > 0) %>%
  select(basin, subbasin, site_name, year, week, Yield_filled_mm_weekly) %>% 
  rename(site_name_little = site_name, yield_little = Yield_filled_mm_weekly) %>% 
  left_join(dat_week_big %>% filter(Yield_filled_mm_weekly > 0) %>%
              select(basin, subbasin, site_name, year, week, Yield_filled_mm_weekly) %>%
              rename(site_name_big = site_name, yield_big = Yield_filled_mm_weekly)) %>%
  filter(!is.na(yield_big), !is.na(yield_little)) %>%
  mutate(yield_little_log = log(yield_little),
         yield_big_log = log(yield_big))
(dat_week_join)
```

View sample size (number of weeks) per site:
```{r}
datatable(dat_week_join %>% group_by(subbasin, site_name_little) %>% summarize(numweeks = n()),
          caption = "Sample size (number of weeks) per site.")
```

```{r}
unique(dat_week_join$subbasin)
```


### View gG - sites combined

::: panel-tabset
#### West Brook
```{r}
dat_week_join %>% filter(subbasin == "West Brook") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Big Creek
```{r}
dat_week_join %>% filter(subbasin == "Big Creek") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Coal Creek
```{r}
dat_week_join %>% filter(subbasin == "Coal Creek") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### McGee Creek
```{r}
dat_week_join %>% filter(subbasin == "McGee Creek") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Paine Run
```{r}
dat_week_join %>% filter(subbasin == "Paine Run") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Staunton River
```{r}
dat_week_join %>% filter(subbasin == "Staunton River") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
#### Donner Blitzen
```{r}
dat_week_join %>% filter(subbasin == "Donner Blitzen") %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, group = site_name_little, color = site_name_little)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  geom_smooth(method = "lm", se = F)
```
:::


### View gG - facet by site

::: panel-tabset
#### West Brook
```{r fig.width=8, fig.height=9}
dat_week_join %>% filter(subbasin == "West Brook") %>% mutate(year = as.factor(year)) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little, ncol = 3, nrow = 4)
```
#### Big Creek
```{r fig.width=8, fig.height=9}
dat_week_join %>% filter(subbasin == "Big Creek") %>% mutate(year = as.factor(year)) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little, ncol = 3, nrow = 4)
```
#### Coal Creek
```{r fig.width=8, fig.height=5}
dat_week_join %>% filter(subbasin == "Coal Creek") %>% mutate(year = as.factor(year)) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little, ncol = 3)
```
#### McGee Creek
```{r fig.width=6, fig.height=3}
dat_week_join %>% filter(subbasin == "McGee Creek") %>% mutate(year = as.factor(year)) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
#### Paine Run
```{r fig.width=8, fig.height=5}
dat_week_join %>% filter(subbasin == "Paine Run") %>% mutate(year = as.factor(year)) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
#### Staunton River
```{r fig.width=8, fig.height=5}
dat_week_join %>% filter(subbasin == "Staunton River") %>% mutate(year = as.factor(year)) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
#### Donner Blitzen
```{r fig.width=6, fig.height=5}
dat_week_join %>% filter(subbasin == "Donner Blitzen") %>% mutate(year = as.factor(year)) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
#### Snake River
```{r fig.width=8, fig.height=7}
dat_week_join %>% filter(subbasin == "Snake River") %>% mutate(year = as.factor(year)) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
#### Shields River
```{r fig.width=8, fig.height=5}
dat_week_join %>% filter(subbasin == "Shields River") %>% mutate(year = as.factor(year)) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
#### Duck Creek
```{r fig.width=6, fig.height=3}
dat_week_join %>% filter(subbasin == "Duck Creek") %>% mutate(year = as.factor(year)) %>%
  ggplot(aes(x = yield_big_log, y = yield_little_log, color = year)) + 
  geom_point(alpha = 0.25) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #geom_smooth(method = "lm", se = F) +
  facet_wrap(~site_name_little)
```
:::




## Write data files

Write daily and weekly paired g-G data to file
```{r}
write_csv(dat_day_join, "C:/Users/jbaldock/OneDrive - DOI/Documents/USGS/EcoDrought/EcoDrought Working/EcoDrought-Analysis/Event Delineation/EcoDrought_Data_Daily_Paired_gG.csv")

write_csv(dat_week_join, "C:/Users/jbaldock/OneDrive - DOI/Documents/USGS/EcoDrought/EcoDrought Working/EcoDrought-Analysis/Event Delineation/EcoDrought_Data_Weekly_Paired_gG.csv")
```



